\documentclass{article}

\input{template/homework/hw-inputs.tex}

\title{
    \vspace{2in}
        % \textmd{\textbf{MT232P - Analysis}}\\
        \textmd{\textbf{MT241P - Finite Mathematics}}\\
        % \textmd{\textbf{MT251P - Foundations of Euclidean Geometry}}\\
    \vspace{1in}
    \textmd{\textbf{Assignment \#4}}\\
    \vspace{1in}
}

\author{
    \hmwkAuthorName\\
    \hmwkStudentnum
}

\date{}

\begin{document}

\maketitle

\pagebreak

\begin{homeworkProblem}
    \homBox{
        Suppose Met Eirann provides the following predictions:\\
        (P1) There is a 60 percent chance that it will rain today.\\
        (P2) There is a 50 percent chance that it will rain tomorrow.
    }
    \part
    \homBox{
        Let 'R' indicate a day with rain and 'N' a day with no rain. List an appro-
        priate sample space $\Omega$.
    }
    \solution
    \part
    \homBox{
        Let A be the event that it rains today and let B be the event that it rains
        tomorrow. List the outcomes of the following events:
        \begin{itemize}
            \item $A^C$
            \item $A\cup B$
            \item $A \cap B$
            \item $A \cap B^C$
            \item $(A \cup B)^C$
        \end{itemize}
    }
    \solution
    \part
    \homBox{
        Find the probabilities for the following events:
        \begin{itemize}
            \item It will rain today or tomorrow.
            \item It will rain today and tomorrow.
            \item It will rain today but not tomorrow.
            \item It will rain today or tomorrow, but not both days.
        \end{itemize}
    }
    \solution
\end{homeworkProblem}
\begin{homeworkProblem}
    \homBox{
        Assume you flip a fair coin with a friend n times, where n $\geq$ 1
    }
    \part
    \homBox{
        How many possible outcomes are there?
    }
    \solution
    \part
    \homBox{
        What is the probability of each outcome?
    }
    \solution
    \part
    \homBox{
        If you throw the coin ten times, what is the chance of there being exactly
        one tail in any three consecutive throws?
    }
    \solution
    \homBox{
        Next you play a game for money. Each time heads comes up you win a Euro, each
time tails comes up you lose a Euro. However, as soon as you lose for the first time
you claim you have to go home and stop playing.
    }
    \part
    \homBox{
        Describe the sample space Ω in terms of your possible wins/losses.
    }
    \solution
    \part
    \homBox{
        For each outcome $\omega \in \Omega$ give its probability.
    }
    \solution
    \part
    \homBox{
        What is the probability of you winning at least one, but less than four Euro?
    }
    \solution
    \part
    \homBox{
        What is the probability of you winning more than two Euro?
    }
    \solution
\end{homeworkProblem}
\begin{homeworkProblem}
    \homBox{
        You are at a party attended by k people, including you. What is the
likelihood of somebody else at the party sharing your birthday? (We assume that
nobody was born in a leap year). What is the likelihood if k = 23?
    }
    \solution
\end{homeworkProblem}
\begin{homeworkProblem}
    \homBox{
        Use combinatorial arguments to prove that, for every integer n $\geq$ 0, $$$$
    }
\end{homeworkProblem}

\end{document}
% \begin{homeworkProblem}
%     \homBox{Hello!}
%     \part
%     \solution
%     \begin{align}
%         Hello
%     \end{align}
%     \begin{align*}
%         Hello
%     \end{align*}
%     \begin{align}
%         Hello
%     \end{align}
%     Hello
%     \part
%     Hello\\Hello\\Hello
%     \solution
%     Hello
% \end{homeworkProblem}


% \begin{homeworkProblem}
%     \defBox{Hello}{
% \begin{itemize}
%     \item It will rain today or tomorrow.
%     \item It will rain today and tomorrow.
%     \item It will rain today but not tomorrow.
%     \item It will rain today or tomorrow, but not both days.
% \end{itemize}
%     }
%     \part
%     \solution

%     \part
%     \solution
% \end{homeworkProblem}


% \begin{homeworkProblem}
%     \lemBox{Hello}{

%     }
% \end{homeworkProblem}


% \begin{homeworkProblem}
%     \thmBox{Hello}{
%         \tcblower
%         Hello
%     }
% \end{homeworkProblem}